Reducing iptables configuration complexity using chains

### 2014-05-07 iptables/presentation.tex
use passive tense
add comma to improve readability
also mention other icmp types

    You can define your own chains

@@

    All rules are checked one by one, and if one matches the target is executed :

@@

    But you can define default target for the predefined chains:

@@

      -A INPUT -p icmp -j ACCEPT \# allow ping\\

>>>>

    Custom chains can be defined

@@

    All rules are checked one by one, and if one matches, the target is executed :

@@

    A default target can be set for the predefined chains:

@@

      -A INPUT -p icmp -j ACCEPT \# allow ping, etc\\
